\documentclass[10pt, aspectratio=169,xcolor=dvipsnames]{beamer}
\usetheme{Simple}
\setbeamersize{text margin left=1.4em,text margin right=1.4em} 

\usepackage{bbm}
\usepackage{bm}
\usepackage{amssymb}
\usepackage{hyperref}
\usepackage{graphicx} % Allows including images
\usepackage{booktabs} % Allows the use of \toprule, \midrule and \bottomrule in tables
\usepackage{fontawesome}
\usepackage{bibentry}
\usepackage[round]{natbib}  
\usepackage{graphicx}
\graphicspath{ {./figures/} } % Allows including images
\usepackage{booktabs} % Allows the use of \toprule, 

\newenvironment{myitemize}{%
   \setlength{\topsep}{0pt}
   \setlength{\partopsep}{0pt}
   %\renewcommand*{\@listi}{\leftmargin\leftmargini %\parsep\z@ \topsep\z@ \itemsep\z@}
   %\let\@listI\@listi
   \itemize
}{\enditemize}


%----------------------------------------------------------------------------------------
%	TITLE PAGE
%----------------------------------------------------------------------------------------

% The title
\title[short title]{How Strong is Your Tinder Game?}
\subtitle{Two-Sided Search in Swipe-Based Dating Platforms}

\author[Patricio Hernandez Senosiain] {Patricio Hernandez Senosiain}
\institute[UofW] 
{
    University of Warwick\\
    EC331 Research in Applied Economics
    \vskip 3pt
}
\date{\today}


%----------------------------------------------------------------------------------------
%	PRESENTATION SLIDES
%----------------------------------------------------------------------------------------

\begin{document}

\begin{frame}
    \titlepage
\end{frame}

\begin{frame}{Overview}
    \tableofcontents
\end{frame}

%----------------------------------------------------------------------------------------
\section{Introduction}
%----------------------------------------------------------------------------------------
\begin{frame}{Introduction – Context, Research Objectives, and Contributions}
\begin{columns}
\begin{column}{0.5\textwidth}
\begin{myitemize}
\setlength\itemsep{1em}
    \item Tinder: a two-sided decentralised matching platform with 70+ million users
    \begin{itemize} 
    \setlength\itemsep{0.5em} 
        \item Agents are presented with suggestions to swipe left or right on; matches occur given a double coincidence of wants 
    \end{itemize} 
    \item Love is a tricky game; Tinder makes it trickier
    \begin{itemize} 
    \setlength\itemsep{0.5em} 
        \item Stage interaction: simple static game of incomplete information
        \item Dynamic interactions are harder due to platform features and repeated game complexities
    \end{itemize}
    
     
    \item \textbf{When should a user `swipe right'?}
    \begin{itemize}
    \setlength\itemsep{0.5em}
        \item What arrangements emerge as equilibria?
        \item How do exogenous factors affect the above?
    \end{itemize}
\end{myitemize}
\end{column} 

\begin{column}{0.5\textwidth}
\begin{myitemize}
\setlength\itemsep{1em}
    \item Related Work
    \begin{itemize}
    \setlength\itemsep{0.5em}
        \item Two-Sided Search: \cite{burdett1998two}, \cite{adachi2003search}, \cite{mekonnen2019random}
        \item Mean Field Games: \cite{jovanovic1988anonymous}, \cite{iyer2014mean}
        \item Modern Dating App Interactions: \cite{kanoria2021facilitating}, \cite{olmeda2021towards}, \cite{DBLP:journals/corr/TysonPHS16}
    \end{itemize}
    
    \item Contributions
    \begin{itemize}
        \setlength\itemsep{0.5em}
        \item One of the first \textit{strategic} models for swipe-based dating platforms. 
        \item An addition to the emerging literature on mean-field game theory.
        \item Case study for computational techniques applied to game theory. 
    \end{itemize}
\end{myitemize}
\end{column}
\end{columns}
\end{frame} 
%----------------------------------------------------------------------------------------
\section{Theoretical Model}
%----------------------------------------------------------------------------------------
\begin{frame}{Theoretical Model – Setup} 
\begin{columns}
\begin{column}{0.5\textwidth}
\begin{myitemize}
\setlength\itemsep{1em}
    \item Time is discrete and indexed $t=0,1,2,...$ %and the market is formed by disjoint sets $\mathcal{M}$ and $\mathcal{W}$ of male and female agents.
    \item Agents are periodically suggested partners from the opposite sex, with attractiveness $\theta_{t} \in \Theta := [0,1]$
    \item Actions $a_t \in\mathcal{A} := \{0,1\}$ are chosen while facing a \textit{swiping budget} $b_t \in \mathcal{B}:=\{0,...,B\}$ that follows LOM: $b_{t+1}=b_t - a_t$
    \item Matching payoff is $u(\theta_{t})$, where $u(\cdot)$ is strictly increasing, bounded, and satisfies $u(0)=0$.
    \item We restrict attention to stationary Markov strategies: $\mu,\omega: \Theta \times \mathcal{B}\rightarrow \Delta \mathcal{A}$
\end{myitemize}
\end{column} 

\begin{column}{0.5\textwidth}
\begin{myitemize}
\setlength\itemsep{1em}
    \item Each period, $\lambda_m$ men and $\lambda_w$ women enter the platform.
    \item Incoming agents' attractiveness is sampled i.i.d from distributions $F_m(\theta)$ and $F_w(\theta)$. 
    \item Agents leave the platform:
    \begin{itemize}
        \item \textit{Endogenously}, when they exhaust their budgets
        \item \textit{Exogenously}, at a death rate of $(1-\delta)$
    \end{itemize}
    \item Let $N^t_m, N^t_w$ denote the masses of men and women in the platform at period $t$.
    \item Let $M^t(\theta,b), W^t(\theta,b)$ be the joint distributions over men and women at $t$.
\end{myitemize}
\end{column}
\end{columns}
\end{frame} 

%----------------------------------------------------------------------------------------

\begin{frame}{Theoretical Model – Characterising the Steady State}
\begin{columns}
\begin{column}{0.45\textwidth}
\begin{myitemize}
\setlength\itemsep{1em} 
    \item The Tinder Market is defined by $\Psi^t=(N_m^t, N_w^t, M^t, W^t)$ 
    \begin{itemize}
        \item Note that this is endogenously dependent on $\mu,\omega$
    \end{itemize}
    \item We seek steady state such that $\Psi^t=\Psi^{t+1}=...=\Psi(\mu,\omega)$
    \item Theorem 1 solves for this, and shows that $\theta$ and $b$ are independent.
    \item Furthermore, it is shown that $M_\theta(\theta;\mu,\omega)= F_m(\theta)$.
    
\end{myitemize}
\end{column}

\begin{column}{0.55\textwidth}
    \begin{theorem}[The Tinder Steady State]
    \small
    
    Fix stationary Markov strategies $\mu,\omega$ and let:
    
    \begin{equation*}
    \rho^m_b=\int_{\Theta}  \mu(\theta',b)\,dW_\theta(\theta';\mu,\omega),
    \end{equation*} 
    \begin{equation*} 
    z^m_b = \prod^{B-b}_{i=1} \frac{\delta\rho^m_{B-i+1}}{\Big(1-\delta (1-\rho^m_{B-i}) \Big)},\quad z^m_B=\Big(1-\delta (1-\rho^m_B)\Big)
    \end{equation*}  
    \par\vspace{0.2cm}
    Then there exists a unique market steady state (with an analogous case for women) characterised by: 
    \par\vspace{0.2cm}
    \begin{equation*} \begin{aligned}N_m(\mu,\omega)&=\lambda_m\left(\frac{z^m_B-\delta z^m_1\rho^m_1}{(1-\delta)z^m_B}\right), \\ M(\theta,b;\mu,\omega)&=F_m(\theta) \left(\frac{(1-\delta)}{z^m_B-\delta z^m_1\rho^m_1}\right)\sum^b_{i=1} z^m_i 
    \end{aligned}
    \end{equation*} 
    \end{theorem} 
\end{column}
\end{columns}
\end{frame} 
%----------------------------------------------------------------------------------------
\begin{frame}{Theoretical Model – The Love Search Problem}
\begin{columns}
\begin{column}{0.45\textwidth}
\begin{myitemize}
\setlength\itemsep{1em}
    \item We consider a man's search problem in a given steady state $\Psi$ against a given $\omega$
    \item With friction-less search, men get suggestions at a rate $\tau=\min\{\frac{N_w}{N_m} ,1\}$ 
    \begin{itemize}
    \setlength\itemsep{0.5em} 
    \item Define $\alpha=\frac{\tau\delta}{1-\delta(1-\tau)}$ as the effective discounting rate
    \end{itemize}
    \item Agents maximise the sum of discounted expected \textit{ex-interim} payoffs $U_m(\theta, a_t)$ 
    \begin{itemize}
    \setlength\itemsep{0.5em} 
    \item The optimal strategy $\widetilde\mu(\theta,b;\omega,\Psi)$ is a cutoff $\widetilde\mu_b$ at the point of indifference
    \end{itemize}
    
    
\end{myitemize}
\end{column}
\begin{column}{0.55\textwidth}
\begin{equation*}
\begin{aligned}V_m(\theta,b)= \max_{\{a_t\}^\infty_{t=0}} \;& \mathbb{E}_{\Psi}\left[\sum^\infty_{t=0} \alpha^{t} U_m(\theta_t,a_t)\;|\; \theta_0,b_0=\theta,b\right]\\ \textrm{s.t.}\; & \theta_t \sim F_w,\quad b_{t+1}  = b_t - a_t \\ &b_t\in \mathcal{B}, \quad a_t\in \mathcal{A} \end{aligned}
\end{equation*}

\begin{equation*}\begin{aligned} V_m(\theta,b) \;=\;\max\Big\{\,& U_m(\theta) +\alpha \,\mathbb{E}_{\Psi}\Big[V_m(\theta', b-1)\Big]\,,\\ & \alpha\,\mathbb{E}_\Psi\Big[ V_m(\theta', b)\Big]\,\Big\} \end{aligned} \end{equation*}  

\end{column} 
\end{columns}
\par\vspace{0.3cm}
\begin{equation}\begin{aligned} u(\widetilde \mu_b) \;=\; \alpha u(\widetilde \mu_b)F_w(\widetilde \mu_b)+\alpha u(\widetilde \mu_{b-1})\Big(1- F_w(\widetilde \mu_{b-1})\Big)+\int^{\widetilde \mu_{b-1}}_{\widetilde \mu_b} \alpha u(\theta')\,dF_w(\theta') \end{aligned}\end{equation}
\begin{equation} u(\widetilde \mu_1)\;=\;\alpha  u(\widetilde\mu_1) F_w(\widetilde\mu_1) + \int^1_{\widetilde\mu_1} \alpha u(\theta')\,dF_w(\theta') \end{equation} 
\end{frame}
%----------------------------------------------------------------------------------------
\begin{frame}{Theoretical Model – Stationary Markov Equilibrium}
\begin{columns}
\begin{column}{0.5\textwidth}  
    \begin{definition}[Stationary Markov Equilibrium]
    \par\vspace{0.4cm} 
    A pair of strategies $\mu^*,\omega^*$ parametrised by cutoffs $\mu^*_b,\, \omega^*_b,\;\forall b \in \mathcal{B}$, and a steady-state market $\Psi^*$ is a Stationary Markov Equilibrium (SME) if:
    \par\vspace{0.4cm} 
    \begin{enumerate}
        \item $\mu^*_b=\widetilde \mu(b;\Psi^*,\omega^*),\quad\forall b\in\mathcal{B}$
        \item $\omega^*_b=\widetilde\omega(b;\Psi^* ,\mu^*),\quad\forall b\in\mathcal{B}$
        \item $\Psi^*= \Psi(\mu^*,\omega^*)$
    \par\vspace{0.4cm}     
\end{enumerate}
    \end{definition} 
\end{column}
\begin{column}{0.5\textwidth}
\begin{myitemize}    
\setlength\itemsep{1em} 
    \item (1) and (2) imply that $\mu^*$ and $\omega^*$ are \textit{ex-ante} best-responses to each other given $\Psi^*$.
    \item (3) implies that $\Psi^*$ is self-consistent: key property of oblivious/mean-field equilibria. 
    \item We solve for this equilibrium computationally by formulating it as a system $\mathbf{E}(\mu,\omega)$ of non-linear equations.
    \item This is then re-framed it as a least-squares optimisation problem that can be solved numerically.
\end{myitemize}
\end{column}
\end{columns}
\end{frame}
%----------------------------------------------------------------------------------------

%----------------------------------------------------------------------------------------
\section{Results}
%------------------------------------------------
\begin{frame}{Results – The Optimal Swiping Rule and Value Function} 
\end{frame}
%----------------------------------------------------------------------------------------
\begin{frame}{Results – Comparative Statics on The Swiping Rule} 
\end{frame}
%----------------------------------------------------------------------------------------
\begin{frame}{Results – Comparative Statics on The Market}  
\end{frame}

%----------------------------------------------------------------------------------------
\section{Reflections and Further Research}
%----------------------------------------------------------------------------------------

%----------------------------------------------------------------------------------------
\begin{frame}{Reflections and Further Research}
\begin{columns}
\begin{column}{0.5\textwidth}
\begin{myitemize}
\setlength\itemsep{1em}  
    \item Cool stuff, but why does it matter?
    \begin{itemize}
    \setlength\itemsep{0.5em}
        \item 6.6 million paid Tinder subscribers by the end of 2020.
        \item Main subscription features: no swiping caps or location limits.
        \item What is the value of subscriptions? Are people wasting their money?  
    \end{itemize}
    
    \item Next Steps: Dynamics
    \begin{itemize}
    \setlength\itemsep{0.5em}
        \item How can the s.s arise as a limiting state?
        \item Best-Response Dynamics? Fictitious Play? 
        \item Bayesian learning?
    \end{itemize}
\end{myitemize}
\end{column} 

\begin{column}{0.5\textwidth}
\begin{myitemize}
\setlength\itemsep{1em}
    \item Next Steps: Noisy Search
    \begin{itemize}
    \setlength\itemsep{0.5em}
        \item How does `profile noise' change the search problem for agents? 
        \item Use of simulations for stability checks
    \end{itemize}
    
    \item Next Steps: Platform Design
    \begin{itemize}
        \setlength\itemsep{0.5em}
        \item How can Tinder set welfare-maximizing swiping caps?
        \item Can directed search mechanisms lead to convergence onto stable matches?
        \item Challenge: limited observability
    \end{itemize}
\end{myitemize}
\end{column}
\end{columns}   
\end{frame}
%----------------------------------------------------------------------------------------

%----------------------------------------------------------------------------------------
\begin{frame}[allowframebreaks]{References}
\bibliographystyle{apalike}
\bibliography{references}
\end{frame}
\end{document}